---
title: "LAB10"
author: "Yingtong Lyu"
date: "November 23, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Write a function that calculates cumulative distribution function of a binomial random variable. Compare results from your function with pbinom() function.

```{r cars}
library(tidyverse)
newpbinom <- function(q, n, p) {
    sum <- 0
    for (i in 0: q) {
        prob <- choose(n, i) * p^i * (1-p)^(n-i)
        sum <- sum + prob
    }
    sum
}
round(pbinom(8,15,0.5),8) == round(newpbinom(8,15,0.5),8)
```

## 2. Write a function that runs simulations to obtain power from a one-sample t-test. Run your function (with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare
your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample').


```{r pressure, echo=FALSE}
newpower <- function(n, delta, sd, sig.level){
    power <- replicate(10000, {
        sample <- rnorm(n, delta, sd)
        test <- as.numeric(t.test(sample, conf.level = (1-sig.level))$p.value < sig.level)
    })
    sum <- sum(power)/10000
    list(n = n, delta = delta, sd = sd, sig.level = sig.level, 
        power = sum, method = "One-sample t test power calculation")
}



# Compare your results with power.t.test()
newpower(n = 100, delta = 0.5, sd = 1, sig.level = 0.05)$power %>% round(3)

power.t.test(n = 100, delta = 0.5, sd = 1, sig.level = 0.05, type = 'one.sample')$power %>% round(3)
```


